A Bayesian Statistical Model Is Able to Predict Target-by-Target Selection Behaviour in a Human Foraging Task

### 2022-11-09 Analysis/index_revisions_2.Rmd
final bits and bobs

#ggsave("../Figures/qjep_preds.pdf", 
#       plt_b2 / (plt1 + plt2) + 
#       plot_layout(guides = "collect") & theme(legend.position = 'bottom'),
#       width = 10, height = 10)

@@

#ggsave("../Figures/qjep_indiv_diff.pdf", 
#       plt_a + plt_b + 
#         plot_layout(widths = c(1, 2)), width = 12, height = 4)
```

@@

```{r}
#ggsave("../Figures/qjep_ex_paths.pdf",
#      ( plts1[[1]] + plts1[[2]]) /( plts3[[1]] + plts3[[3]]), 
#       width = 8, height = 8)

@@

```{r}
#ggsave("../Figures/path_length.pdf", plt2 + plt2b, width = 8, height = 3)
```

@@

create_post_plot("x") + create_post_plot("y") + plt_mu #& theme_bw()
#ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
```

@@

(plt_x + plt_y) + plt_lambdas

@@

plt1 / (plt2 + plt3)  + plot_layout(guides = "collect")

#ggsave("../Figures/qjep_init_sel_preds.pdf",
#       width = 8, height = 4)

>>>>

#ggsave("../Figures/qjep_preds.pdf", 
#       plt_b2 / (plt1 + plt2) + plot_annotation(tag_levels = list(c('(a)', '(b)', '(c)'))) +
#       plot_layout(guides = "collect") & theme(legend.position = 'bottom'),
#       width = 10, height = 10)

@@

#ggsave("../Figures/qjep_indiv_diff.pdf", 
#       plt_a + plt_b + plot_annotation(tag_levels = list(c('(a)', '(b)'))) +
#         plot_layout(widths = c(1, 2)), width = 12, height = 4)
```

@@

```{r}
#ggsave("../Figures/qjep_ex_paths.pdf",
#      ( plts1[[1]] + plts1[[2]]) /( plts3[[1]] + plts3[[3]])  + plot_annotation(tag_levels = list(c('(a)', '(b)', '(c)', '(d)'))),
#       width = 8, height = 8)

@@

```{r}
#ggsave("../Figures/path_length.pdf", plt2 + plt2b + plot_annotation(tag_levels = list(c('(a)', '(b)'))), width = 8, height = 3)
```

@@

create_post_plot("x") + create_post_plot("y") + plt_mu + plot_annotation(tag_levels = list(c('(a)', '(b)', '(c)'))) #& theme_bw() 
#ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
```

@@

(plt_x + plt_y) + plt_lambdas + plot_annotation(tag_levels = list(c('(a)', '(b)', '(c)')))

@@

plt1 / (plt2 + plt3)  + plot_layout(guides = "collect")  + plot_annotation(tag_levels = list(c('(a)', '(b)', '(c)')))

#ggsave("../Figures/qjep_init_sel_preds.pdf",
#       width = 10, height = 6)

### 2022-11-09 Proofs/vision-1871367-proofreading.tex
final bits and bobs

\hl{Foraging}, the act of searching for and gathering multiple targets (such as food), has been studied in both nonhuman animal contexts \cite{dawkins1971} and in human psychology studies~\cite{kristjansson2014}. Foraging engages a wide range of different perceptual, cognitive, decision-related and motor skills, and is an ecologically relevant behaviour for most species, including humans. For these and other reasons, a sustained interest in foraging has developed our understanding of how we search for multiple instances of multiple types of targets. For example, the classic marginal value theorem \cite {charnov1976} is generally good at predicting when an organism will decide to stop searching in a patch and move on to another, based on the finding rate dropping below an expected rate, and taking into account the relative energy costs of traveling between patches versus staying within a patch. There has also been a concerted effort to characterize the spatial patterns of foraging behaviour. The Lévy Walk, for example, has been argued to be a good description of the foraging path many species take when the locations of targets are unknown (e.g., \citep {bartumeus2005}, but see also \citep{benhamou2007}). %MDPI:Please make sure that all genes and species names as well as all the variables like "p" or "n" are written in italic font. Protein names, Latin words and genera/families should be kept in a normal font. Greek/Latin expressions and non-common foreign words and phrases should NOT be in Italic format.
%MDPI:  Abbreviations need to be defined, on their first mention, once in the Abstract, once in the Main Text, once in Figures' description, and once in the Tables' footer. Abbreviations used as keywords should be defined too.Please check and make sure that this rule is applied through the whole paper.

@@

Different aspects of foraging behaviour, such as the search image and the search path, clearly interact with one another, but most research has tried to understand them separately. In many cases, the pattern of foraging behaviour has been studied using aggregate measures calculated on the level of a trial, such as the mean number of 'runs' (where the same type of target is selected multiple times in a row) or the total number of targets found during the longest run. These summary statistics can provide a broad view of switching behaviour, but they can also be biased by the spatial distribution of target types, and by a forager's preference for one target or another. To address the need for a more precise set of measurements, we recently developed a new model to analyse foraging data, based on a sampling without replacement procedure \cite{clarke2022foraging}. By using this model, we demonstrated that we were able to break down foraging into a number of different cognitive biases, such as a preference to stick to the same target type, or a preference for nearby targets, and used this model to successfully reanalyse data from a number of open access datasets \cite{kristjansson2014, thornton2022, clarke2022, tagu_kristjansson_2021}.

@@

These combine to give:
\begin{linenomath}
\begin{equation}
    w_i = g\left(b_at_i + b_sm(t_i, t_{i-1})\right) \times \rho_d(i, i-1) \rho_{\theta}(i, i-1)
\end{equation}
\end{linenomath}
where $t_i = 1$ if item $i$ is of class $A$ and 0 otherwise, and  $m(t_i, t_{i-1}) =1$ if item $i$ is the same class as the previously selected item. $\rho_d$ and $\rho_{\theta}$ measure proximity and the effect of~direction:
\begin{linenomath}
\begin{equation}
    \rho_d = e^{-\sigma_dd(i,j)}
\end{equation}
\end{linenomath}
\begin{linenomath}
\begin{equation}
    \rho_{\theta} = e^{-\sigma_d\theta(i,j)}
\end{equation}
\end{linenomath}
$d(i,j)$ is simply the Euclidean distance between items $i$ and $j$, while $\theta$ is defined as:
\begin{linenomath}
\begin{equation}
    \theta(i,j) = \frac{f(\text{atan2}(i, j) - \text{atan2}(i-1, i))}{\pi}
\end{equation}
\end{linenomath}
with $f(\phi_1, \phi_2) = \text{min}((\phi_1 - \phi_2) \% 2\pi, (\phi_2 - \phi_1) \% 2\pi)$ calculating the angular difference. $\text{atan2}$ is the direction of travel from i to j.  This model is implemented in a multilevel framework, allowing each of the four parameters to vary from participant to participant. Further details including priors and full code can be found with \cite{clarke2022foraging}.

@@

We mainly \hl{used} R v4.2.0 and rStan v2.26.11 \cite{rstan} (R Foundation for Statistical Computing, Vienna, Austria). For fitting the model to the data from~\cite{clarke2022} we used a university computing cluster with R v3.6.3 and rStan v2.19.2.%MDPI:For all equipment/software/products used, the following information should be given: company name, city, state abbreviation (if its from USA or Canada), and country must be provided. Please apply this rule through the whole Materials and Methods section

@@

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=17.8 cm]{Figures/qjep_preds.pdf}
\end{adjustwidth}
\caption{({\textbf{\hl{top left}}}) Posterior probabilities for target selections during a visual foraging task. Each dot shows the data from an individual participant, averaged over trials, in the feature condition and the shaded region indicates the interval in which we expect 67\% of participants to fall. The dashed line indicates chance performance. (\textbf{\hl{top right}}) As top left, except showing the conjunction condition. (\textbf{\hl{bottom left}})  Calibration plot for our foraging model. The $x$-axis gives the largest weight assigned by the model while the $y$-axis shows how often that target was actually selected by a human participant. The dashed line here and in the right plot is the identity line. (\textbf{\hl{bottom right}}) This plot shows how often the model selects the 2nd and 3rd ranked items based on the weights assigned by the model.} %mdpi: we removed the subfigure label from italic to be not italic and added bold of it according to our rule, please confirm, same in below figures. RESPONSE: Confirmed.

% Also, please divide the figure into 4 subfigures and  note them accordingly. Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole. Subfigures should be provided with sub-caption and put sub-caption in figure caption.

@@

\begin{figure}[H]
\includegraphics[width=13.5 cm]{Figures/qjep_indiv_diff.pdf}
\caption{({\textbf{\hl{left}}}) Prediction scores for participants. Boxplots show quartile range and the grey lines indicate individual participants. The dots indicate outliers. (\textbf{\hl{right}}) How accuracy of our model varies with the strength of an individual’s \textit{bM}, \textit{bP}, \textit{pA} and \textit{pS} parameters. We can see two clear outlier participants (marked with an X).} %MDPI: please divide the figure into 2 subfigures and  note them accordingly. Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole. Subfigures should be provided with sub-caption and put sub-caption in figure caption.
%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors. If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it.Thank you for your cooperation! RESPONSE: Confirmed.

@@

\begin{figure}[H]
\includegraphics[width=12 cm]{Figures/qjep_ex_paths.pdf}
\caption{(\textbf{\hl{top}}) Two randomly selected trials in which the model does a good job in accounting for human behaviour. The numbers indicate the order the participant selected targets in. Red arrows indicate places where the model prediction deviates from participant behaviour. When participants diverge from the model's prediction, it appears to be due to some form of path-length optimisation. (\textbf{\hl{bottom}}) Two randomly selected examples in which the model does a less good job in accounting for the order in which human participants selected the items.}%MDPI: please divide the figure into subfigures and  note them accordingly. Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole. Subfigures should be provided with sub-caption and put sub-caption in figure caption. Please add explanation for all the symbols/colors
%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors. If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it. Thank you for your cooperation! RESPONSE: Confirmed

@@

For trials in which the model does a worse job of predicting (accuracy <50$\%$) we can see that the human behaviour appears less organised in terms of proximity in general and it seems unlikely that adding some form of path-length optimisation to our model would improve accuracy with these participants. We can see this more clearly in Figure \ref{fig:qjep_path_lengths}: while our model does a good job of capturing the average total path length, there is considerable variation with some participants generating shorter paths and some longer. We can see  that this appears to be systematically related to how well our model can predict behaviour. Interestingly, in some cases, poorly predicted trials appear to have very strong pS biases, collecting all exemplars of one target and then the other: thus, the participants are carrying out a strategy that the model is not capturing well. This fits with conjunction trials being harder for the model to predict, as these trials generally have fewer switches. 
\vspace{-10pt}
\begin{figure}[H]
\includegraphics[width=13.5 cm]{Figures/path_length.pdf}
\caption{({\textbf{\hl{left}}}) Histogram showing the distribution of the median path lengths for our human participants and model (fitted to each human participant via the random effect structure). (\textbf{\hl{right}}) The relationship between model accuracy and the proportion of trials in which the human participant has a shorter total path length than predicted.}%MDPI:please divide the figure into 2 subfigures and  note them accordingly. Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole. Subfigures should be provided with sub-caption and put sub-caption in figure caption.
%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors. If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it. Thank you for your cooperation! RESPONSE: Confirmed

@@

\begin{figure}[H]
\includegraphics[width=12 cm]{Figures/init_sel_hex_plot.pdf}
\caption{Hexagonal heatmaps showing the two-dimensional distribution of the location of initial target selections. Grey areas indicate cells with a count of 0. ({\textbf{\hl{left}}}) shows the distribution over all initial target selections (i.e., multiple trials per participant) while ({\textbf{\hl{right}}}) shows the distribution of each participant's median initial selection (i.e., each participant contributes one data point to the~graph). }%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors. If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it. Thank you for your cooperation! RESPONSE: Confirmed.

@@

The results are shown in Figure \ref{fig:qjep_init_sel_mdl} and we can clearly see that most participants either have a strong bias to $x=0$ and $y=0$, or a more diffuse central bias. 
\vspace{-6pt}
\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=17.5 cm]{Figures/init_sel_mdl.pdf}
\end{adjustwidth}
\caption{Posterior fits for ({\textbf{\hl{left}}}) horizontal and ({\textbf{\hl{middle}}}) vertical locations of the initial target selection. Each line represents a different participant. ({\textbf{\hl{right}}}) A scatter plot showing the $x$ and $y$ posterior means for each participant.}%MDPI: please divide the figure into 3 subfigures and  note them accordingly. Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole. Subfigures should be provided with sub-caption and put sub-caption in figure caption.
%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors. If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it. Thank you for your cooperation! RESPONSE: Confirmed

@@

The model fit is shown in Figure \ref{fig:qjep_init2_sel_mdl}. We can see that the two components identified by the model clearly correspond to the top corner and diffuse-central strategies discussed above. We can also see from the lambda values that our participants take on a range of different mixtures between the two. 
\vspace{-12pt}
\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}%\centering
\centering
\includegraphics[width=1.3\textwidth]{Figures/init_sel2_mdl.pdf}
\end{adjustwidth}
\caption{Posterior fits for the ({\textbf{\hl{left}}}) horizontal and ({\textbf{\hl{middle}}}) vertical locations of the initial target selection. ({\textbf{\hl{right}}}) shows the mixing parameters for each participant, with the error bar indicating the $95\%$ HDPI.}%MDPI:Please define "x" and "y" from subfigures 1 and 2. Also, please divide the figure into 3 subfigures. Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole. Subfigures should be provided with sub-caption and put sub-caption in figure caption.
%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors. If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it. Thank you for your cooperation! RESPONSE: Confirmed

@@

To compare the two approaches, we assess how well they fit the empirical data: we can use the fitted distributions to calculate the weight assigned to the selected target by each method for each trial in our dataset (\hl{Figure} \ref{fig:qjep_init_sel_pred}). We can see that both models give a similar distribution of target weights and accuracies. Overall, both methods  select the correct target in around half of the trials. Interestingly, as above, there is considerable variation between participants, with participants who favour the top-left corner being easier to predict. %MDPI: Please move Figure 8 right after this paragraph ends(Figures and tables need to appear in exact numerical order, right after their first citation)

@@

\begin{figure}[H]
\includegraphics[width=13.8 cm]{Figures/qjep_init_sel_preds.pdf}
\caption{({\textbf{\hl{Top}}}): a count of initial weight values predicted from both methods (mixture and multi-level). ({\textbf{\hl{Bottom left}}}): the proportion of times the first selection was correct for both methods.  ({\textbf{\hl{Bottom right}}}): as lambda (the model parameter underlying initial weight) increases, accuracy increases i.e., the model is more accurate for the cases where participants are selecting a corner as their initial target selection. The dots each represent an individual participant, and the line is the line of best fit.}% MDPI: please divide the figure into 2 subfigures and  note them accordingly. Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole. Subfigures should be provided with sub-caption and put sub-caption in figure caption.
%MDPI: Please provide a short explanation for the black dots from the 3rd subfigure RESPONSE: Done
%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors. If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it. Thank you for your cooperation! RESPONSE: Confirmed

@@

Our exploratory analyses seem to hint at the idea that the people who are difficult for the model to predict are those who do not behave in a manner that optimises path length. It could be that these participants are simply unpredictable, and do not behave in a consistent manner on a target-by-target basis, making it difficult for a model to predict their behaviour at this level of granularity. However, it is possible that there are other factors that we have not taken into account that could further help explain these discrepancies. Participants who 'stick' to one type of target are likely to have longer path lengths, and it seems that the model does do a poorer job of predicting conjunction trials, which generally have stronger pS biases. Thus, one area for future improvement of the model is to try to capture this behaviour better: it may be that a 'floor' parameter (on a participant-by-participant basis) in the spatial fall off, allocating more weight to more distant targets, may help account for currently difficult to predict trial behaviour.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\supplementary{\hl{The following are available online at} \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}
%mdpi: please fully complete this part with information regarding  supplementary materials, as shown in the above example.

@@

\dataavailability{Data supporting reported results can be found on Github at XXX. The datasets analysed in this study can be found at \url{https://osf.io/y6qbv/}, \hl{accessed on}, and \linebreak  \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0100752}, \hl{accessed on}.} 
%MDPI: Please add the access date (Format: Date Month Year). e.g., (accessed on 1 January 2020).

>>>>

\hl{Foraging}, the act of searching for and gathering multiple targets (such as food), has been studied in both nonhuman animal contexts \cite{dawkins1971} and in human psychology studies~\cite{kristjansson2014}. Foraging engages a wide range of different perceptual, cognitive, decision-related and motor skills, and is an ecologically relevant behaviour for most species, including humans. For these and other reasons, a sustained interest in foraging has developed our understanding of how we search for multiple instances of multiple types of targets. For example, the classic marginal value theorem \cite {charnov1976} is generally good at predicting when an organism will decide to stop searching in a patch and move on to another, based on the finding rate dropping below an expected rate, and taking into account the relative energy costs of traveling between patches versus staying within a patch. There has also been a concerted effort to characterize the spatial patterns of foraging behaviour. The Lévy Walk, for example, has been argued to be a good description of the foraging path many species take when the locations of targets are unknown (e.g., \citep {bartumeus2005}, but see also \citep{benhamou2007}). %MDPI:Please make sure that all genes and species names as well as all the variables like "p" or "n" are written in italic font. Protein names, Latin words and genera/families should be kept in a normal font. Greek/Latin expressions and non-common foreign words and phrases should NOT be in Italic format.
%MDPI:  Abbreviations need to be defined, on their first mention, once in the Abstract, once in the Main Text, once in Figures' description, and once in the Tables' footer. Abbreviations used as keywords should be defined too.Please check and make sure that this rule is applied through the whole paper.
% RESPONSE: Checked.

@@

Different aspects of foraging behaviour, such as the search image and the search path, clearly interact with one another, but most research has tried to understand them separately. In many cases, the pattern of foraging behaviour has been studied using aggregate measures calculated on the level of a trial, such as the mean number of 'runs' (where the same type of target is selected multiple times in a row) or the total number of targets found during the longest run. These summary statistics can provide a broad view of switching behaviour, but they can also be biased by the spatial distribution of target types, and by a forager's preference for one target or another. To address the need for a more precise set of measurements, we recently developed a new model to analyse foraging data, based on a sampling without replacement procedure \cite{clarke2022foraging}. By using this model, we demonstrated that we were able to break down foraging into a number of different cognitive biases, such as a preference to stick to the same target type, or a preference for nearby targets, and used this model to successfully reanalyse data from a number of open access datasets \cite{kristjansson2014, thornton2022foraging, clarke2022, tagu_kristjansson_2021}.

@@

These combine to give:
\begin{linenomath}
\begin{equation}
    w_i = g\left(b_at_i + b_sm(t_i, t_{i-1})\right) \times \rho_d(i, i-1) \rho_{\theta}(i, i-1)
\end{equation}
\end{linenomath}
where $t_i = 1$ if item $i$ is of class $A$ and 0 otherwise, and  $m(t_i, t_{i-1}) =1$ if item $i$ is the same class as the previously selected item. $\rho_d$ and $\rho_{\theta}$ measure proximity and the effect of~direction:
\begin{linenomath}
\begin{equation}
    \rho_d = e^{-\sigma_dd(i,j)}
\end{equation}
\end{linenomath}
\begin{linenomath}
\begin{equation}
    \rho_{\theta} = e^{-\sigma_d\theta(i,j)}
\end{equation}
\end{linenomath}
$d(i,j)$ is simply the Euclidean distance between items $i$ and $j$, while $\theta$ is defined as:
\begin{linenomath}
\begin{equation}
    \theta(i,j) = \frac{f(\text{atan2}(i, j) - \text{atan2}(i-1, i))}{\pi}
\end{equation}
\end{linenomath}
with $f(\phi_1, \phi_2) = \text{min}((\phi_1 - \phi_2) \% 2\pi, (\phi_2 - \phi_1) \% 2\pi)$ calculating the angular difference. $\text{atan2}$ is the direction of travel from \textit{i} to \textit{j}.  This model is implemented in a multilevel framework, allowing each of the four parameters to vary from participant to participant. Further details including priors and full code can be found with \cite{clarke2022foraging}.

@@

We mainly \hl{used} R v4.2.0 and rStan v2.26.11 \cite{rstan} (R Foundation for Statistical Computing, Vienna, Austria). For fitting the model to the data from~\cite{clarke2022} we used a university computing cluster with R v3.6.3 and rStan v2.19.2.%MDPI:For all equipment/software/products used, the following information should be given: company name, city, state abbreviation (if its from USA or Canada), and country must be provided. Please apply this rule through the whole Materials and Methods section RESPONSE: Done.

@@

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=17.8 cm]{Figures/qjep_preds.pdf}
\end{adjustwidth}
\caption{({\textbf{\hl{a}}}) Top left: Posterior probabilities for target selections during a visual foraging task. Each dot shows the data from an individual participant, averaged over trials, in the feature condition and the shaded region indicates the interval in which we expect 67\% of participants to fall. The dashed line indicates chance performance. Top right: As top left, except showing the conjunction condition. (\textbf{\hl{b}})  Calibration plot for our foraging model. The $x$-axis gives the largest weight assigned by the model while the $y$-axis shows how often that target was actually selected by a human participant. The dashed line here and in the right plot is the identity line. (\textbf{\hl{c}}) This plot shows how often the model selects the 2nd and 3rd ranked items based on the weights assigned by the model.} %mdpi: we removed the subfigure label from italic to be not italic and added bold of it according to our rule, please confirm, same in below figures. RESPONSE: Confirmed.

% Also, please divide the figure into 4 subfigures and  note them accordingly. Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole. Subfigures should be provided with sub-caption and put sub-caption in figure caption. RESPONSE: Done.

@@

\begin{figure}[H]
\includegraphics[width=13.5 cm]{Figures/qjep_indiv_diff.pdf}
\caption{({\textbf{\hl{a}}}) Prediction scores for participants. Boxplots show quartile range and the grey lines indicate individual participants. The dots indicate outliers. (\textbf{\hl{b}}) How accuracy of our model varies with the strength of an individual’s \textit{bM}, \textit{bP}, \textit{pA} and \textit{pS} parameters. We can see two clear outlier participants (marked with an X).} %MDPI: please divide the figure into 2 subfigures and  note them accordingly. Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole. Subfigures should be provided with sub-caption and put sub-caption in figure caption. RESPONSE: Done.
%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors. If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it.Thank you for your cooperation! RESPONSE: Confirmed.

@@

\begin{figure}[H]
\includegraphics[width=12 cm]{Figures/qjep_ex_paths.pdf}
\caption{(\textbf{\hl{a}}) and (\textbf{\hl{b}}) Two randomly selected trials in which the model does a good job in accounting for human behaviour. The numbers indicate the order the participant selected targets in. Red arrows indicate places where the model prediction deviates from participant behaviour. When participants diverge from the model's prediction, it appears to be due to some form of path-length optimisation. (\textbf{\hl{c}}) and (\textbf{\hl{d}}) Two randomly selected examples in which the model does a less good job in accounting for the order in which human participants selected the items.}%MDPI: please divide the figure into subfigures and  note them accordingly. Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole. Subfigures should be provided with sub-caption and put sub-caption in figure caption. Please add explanation for all the symbols/colors RESPONSE: Done
%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors. If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it. Thank you for your cooperation! RESPONSE: Confirmed

@@

For trials in which the model does a worse job of predicting (accuracy <50$\%$) we can see that the human behaviour appears less organised in terms of proximity in general and it seems unlikely that adding some form of path-length optimisation to our model would improve accuracy with these participants. We can see this more clearly in Figure \ref{fig:qjep_path_lengths}: while our model does a good job of capturing the average total path length, there is considerable variation with some participants generating shorter paths and some longer. We can see  that this appears to be systematically related to how well our model can predict behaviour. Interestingly, in some cases, poorly predicted trials appear to have very strong \textit{pS} biases, collecting all exemplars of one target and then the other: thus, the participants are carrying out a strategy that the model is not capturing well. This fits with conjunction trials being harder for the model to predict, as these trials generally have fewer switches. 
\vspace{-10pt}
\begin{figure}[H]
\includegraphics[width=13.5 cm]{Figures/path_length.pdf}
\caption{({\textbf{\hl{a}}}) Histogram showing the distribution of the median path lengths for our human participants and model (fitted to each human participant via the random effect structure). (\textbf{\hl{b}}) The relationship between model accuracy and the proportion of trials in which the human participant has a shorter total path length than predicted.}%MDPI:please divide the figure into 2 subfigures and  note them accordingly. Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole. Subfigures should be provided with sub-caption and put sub-caption in figure caption. RESPONSE: Done
%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors. If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it. Thank you for your cooperation! RESPONSE: Confirmed

@@

\begin{figure}[H]
\includegraphics[width=12 cm]{Figures/init_sel_hex_plot.pdf}
\caption{Hexagonal heatmaps showing the two-dimensional distribution of the location of initial target selections. Grey areas indicate cells with a count of 0. The left panel shows the distribution over all initial target selections (i.e., multiple trials per participant) while the right panel shows the distribution of each participant's median initial selection (i.e., each participant contributes one data point to the~graph). }%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors. If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it. Thank you for your cooperation! RESPONSE: Confirmed.

@@

The results are shown in Figure \ref{fig:qjep_init_sel_mdl} and we can clearly see that most participants either have a strong bias to $x=0$ and $y=0$, or a more diffuse central bias. 
\vspace{-6pt}
\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=17.5 cm]{Figures/init_sel_mdl.pdf}
\end{adjustwidth}
\caption{Posterior fits for ({\textbf{\hl{a}}}) horizontal and ({\textbf{\hl{b}}}) vertical locations of the initial target selection. Each line represents a different participant. ({\textbf{\hl{c}}}) A scatter plot showing the $x$ and $y$ posterior means for each participant.}%MDPI: please divide the figure into 3 subfigures and  note them accordingly. Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole. Subfigures should be provided with sub-caption and put sub-caption in figure caption. RESPONSE: Done
%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors. If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it. Thank you for your cooperation! RESPONSE: Confirmed

@@

The model fit is shown in Figure \ref{fig:qjep_init2_sel_mdl}. We can see that the two components identified by the model clearly correspond to the top corner and diffuse-central strategies discussed above. We can also see from the lambda values that our participants take on a range of different mixtures between the two. 
\vspace{-12pt}
\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}%\centering
\centering
\includegraphics[width=1.3\textwidth]{Figures/init_sel2_mdl.pdf}
\end{adjustwidth}
\caption{Posterior fits for the ({\textbf{\hl{a}}}) horizontal and ({\textbf{\hl{b}}}) vertical locations of the initial target selection. ({\textbf{\hl{c}}}) shows the mixing parameters for each participant, with the error bar indicating the $95\%$ HDPI.}%MDPI:Please define "x" and "y" from subfigures 1 and 2. Also, please divide the figure into 3 subfigures. Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole. Subfigures should be provided with sub-caption and put sub-caption in figure caption. RESPONSE: Done
%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors. If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it. Thank you for your cooperation! RESPONSE: Confirmed

@@

To compare the two approaches, we assess how well they fit the empirical data: we can use the fitted distributions to calculate the weight assigned to the selected target by each method for each trial in our dataset (\hl{Figure} \ref{fig:qjep_init_sel_pred}). We can see that both models give a similar distribution of target weights and accuracies. Overall, both methods  select the correct target in around half of the trials. Interestingly, as above, there is considerable variation between participants, with participants who favour the top-left corner being easier to predict. %MDPI: Please move Figure 8 right after this paragraph ends(Figures and tables need to appear in exact numerical order, right after their first citation) RESPONSE: Done

\begin{figure}[H]
\includegraphics[width=13.8 cm]{Figures/qjep_init_sel_preds.pdf}
\caption{({\textbf{\hl{a}}}): a count of initial weight values predicted from both methods (mixture and multi-level). ({\textbf{\hl{b}}}): the proportion of times the first selection was correct for both methods.  ({\textbf{\hl{c}}}): as lambda (the model parameter underlying initial weight) increases, accuracy increases i.e., the model is more accurate for the cases where participants are selecting a corner as their initial target selection. The dots each represent an individual participant, and the line is the line of best fit.}% MDPI: please divide the figure into 2 subfigures and  note them accordingly. Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole. Subfigures should be provided with sub-caption and put sub-caption in figure caption.
%MDPI: Please provide a short explanation for the black dots from the 3rd subfigure RESPONSE: Done
%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors. If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it. Thank you for your cooperation! RESPONSE: Confirmed

@@

@@

Our exploratory analyses seem to hint at the idea that the people who are difficult for the model to predict are those who do not behave in a manner that optimises path length. It could be that these participants are simply unpredictable, and do not behave in a consistent manner on a target-by-target basis, making it difficult for a model to predict their behaviour at this level of granularity. However, it is possible that there are other factors that we have not taken into account that could further help explain these discrepancies. Participants who 'stick' to one type of target are likely to have longer path lengths, and it seems that the model does do a poorer job of predicting conjunction trials, which generally have stronger \textit{pS} biases. Thus, one area for future improvement of the model is to try to capture this behaviour better: it may be that a 'floor' parameter (on a participant-by-participant basis) in the spatial fall off, allocating more weight to more distant targets, may help account for currently difficult to predict trial behaviour.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\supplementary{\hl{The following are available online at} \linksupplementary{s1}, Document S1: Supplementary Materials 1, Document S2: Supplementary Materials 2}
%mdpi: please fully complete this part with information regarding  supplementary materials, as shown in the above example. RESPONSE: Done

@@

\dataavailability{Data supporting reported results can be found on Github at \url{https://github.com/scienceanna/foraging_svg}. The datasets analysed in this study can be found at \url{https://osf.io/y6qbv/}, \hl{accessed on 25th April 2022}, and \linebreak  \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0100752}, \hl{accessed on 27th May 2022}.} 
%MDPI: Please add the access date (Format: Date Month Year). e.g., (accessed on 1 January 2020). RESPONSE: Done.
